State of the Art in Concurrent Priority Queues \\ Student Paper for Seminar in Algorithms 2013W \\ Technical University of Vienna

### 2014-03-17 paper/paper.tex
Related work

@@

% Bounded priority queues
% PQ's with non-available primitives
% Other relaxed data structures -> k-FIFO
% ... ?

>>>>

% TODO: Memory management.

@@

There have been many publications on more specialized variants of concurrent priority queues
which we did not cover in this paper.

% PQ's with non-available primitives

\citeauthor{liu2012lock} present a lock-free, array-based priority queue in \cite{liu2012lock}
using the non-standard \ac{DCAS} and \ac{DCSS} instructions. In addition to the standard
\lstinline|Insert| and \lstinline|DeleteMin| operations, it also provides an \lstinline|ExtractMany|
function which returns the $n$ highest priority items in the queue, and a function that returns
items which ``probably'' have high priority. Other implementations based on non-standard instructions
can be found in \cite{israeli1993efficient,greenwald1999non}.

% Bounded priority queues

Another possibility is the restriction of priorities to a particular set, i.e. bounded range priorities.
\citeauthor{shavit1999scalable} present two such data structures in \cite{shavit1999scalable} using
combining funnels and bins of items.

% PQ's in message passing systems (see SprayList reviews)

Concurrent priority queues have also been studied in other contexts such as distributed memory systems.
\citeauthor{karp1993randomized} describe a distributed priority queue in which each processor owns
a local priority queue, inserts are sent to a random priority queue, and \lstinline|DeleteMin| operations
simply access the local queue \cite{karp1993randomized}.
\citeauthor{sanders1998randomized} extends this idea to remove the globally best elements instead
\cite{sanders1998randomized}.

% Other relaxed data structures -> k-FIFO

Finally, the principle of relaxation has also been applied to other data structures.
\citeauthor{kirsch2012fast} invented an efficient k-FIFO queue \cite{kirsch2012fast},
% TODO: More cites.
